---
title: The Association Between Modern Media and Public Opinions
author: 
date: "`r Sys.Date()`"
output: html_document
---

##Summary and Purpose of Study:  
The data was collected using two online surveys between the months of August and December of 2012. Political affiliation, social standing, and stance on common issues were all examined and measured quantitatively throughout two surveys that were dispersed within 4 months. Participants were asked to rate certain social and political issues presented often by asking them their opinions on a score from one to one hundred percent. The sample targeted African American/Black males over 18, African American/Black females over 18, Causasian/White males over 18, and Caucasian/White females over 18. Participants were chosen from the GfK knowledge network, which is a online panel that is supposed to represent the population of the United States. The data highlighted here is political interest, how often they keep themselves up-to-date on current events, and political affiliation. For this study, I have referenced the Outlook On Life dataset. 

The purpose of this study is to examine whether modern media has an effect on the opinions of the citizens of the United States. The goals of this study are to (1) establish a relationship between Americans and media and (2) determine if American attitudes are swayed by the media.  

##Variables:  
Variables I have considered in my data include W1_A1 (how interested participants are in what is going on in politics and government), W1_A2 (have participants thought about the upcoming election of 2012 recently), W1_A11 (how many times participants have watched national news programs on TV or on the Internet in the past week), and W1_C1 (what do participants identify as: Democratic, Republican, Independent, or other).    



```{r comment = NA}
library(PDS)
library(dplyr)
OOL.sub <- OOL %>% 
   rename(InterestPol = W1_A1, ThoughtsElections = W1_A2, WatchNews = W1_A11, PoliticalAffil = W1_C1, Welfare = W1_N1A, Congress = W1_N1I) 
OOL.sub$InterestPol[OOL.sub$InterestPol == -1] <- NA
OOL.sub$InterestPol <- factor(OOL.sub$InterestPol,labels=c("Extremely","Very", "Moderately Interested", "Slightly", "Not Interested"))
table(OOL.sub$InterestPol)
OOL.sub$ThoughtsElections[OOL.sub$ThoughtsElections == -1] <- NA
OOL.sub$ThoughtsElections <- factor(OOL.sub$ThoughtsElections,labels=c( "Quite a lot", "Somewhat a lot", "Somewhat a little", "Only a little", "Not at all"))
table(OOL.sub$ThoughtsElections)
OOL.sub$WatchNews[OOL.sub$WatchNews == -1] <- NA
OOL.sub$WatchNews <- factor(OOL.sub$WatchNews,labels=c ("None", "One Day", "Two Days", "Three Days", "Four Days", "Five Days", "Six Days", "Seven Days"))
table(OOL.sub$WatchNews)
OOL.sub$PoliticalAffil[OOL.sub$PoliticalAffil == -1] <- NA
OOL.sub$Welfare[OOL.sub$Welfare == 998] <- NA
OOL.sub$Congress[OOL.sub$Congress == 998] <- NA
OOL.sub$PoliticalAffil <- factor(OOL.sub$PoliticalAffil, labels=c("Republican", "Democratic", "Independent", "Something Else"))
table(OOL.sub$PoliticalAffil)
OOL.sub <- OOL.sub %>%
   select(InterestPol, ThoughtsElections, WatchNews, PoliticalAffil, Welfare, Congress)
```


#Bar Graphs
```{r}
library(ggplot2)
g1 <- ggplot(data = na.omit(OOL.sub), aes(WatchNews)) +
  geom_bar(fill = c("green")) +
  labs(x = "", y = "Total Number", title = "How Many Times a Week Do You Watch the News?") +
  theme_bw() + 
  theme(axis.text.x  = element_text(angle = 75, vjust = 0.5)) 
g1
```
This is a graph of the variable "How Many Times a Week Do You Watch the News?". This graph shows the answers of participants when asked how often they watch the news in a week. Most participants either do not watch the news at all or they watch the news seven times a week. 

```{r}
g2 <- ggplot(data = na.omit(OOL.sub), aes(InterestPol)) +
  geom_bar(fill = c("magenta")) +
  labs(x = "", y = "Total Number", title = "How Interested Are You in Politics?") +
  theme_bw() + 
  theme(axis.text.x  = element_text(angle = 75, vjust = 0.5)) 
g2
```
This is a graph of the variable "How Interested Are You In Politcs?". This graph shows the answers of participants when asked if they were at all interested in politics and if so, how interested were they. Most participants said they were "Very Interested" or "Moderately Interested". It is unexpected to see that most are "Very Interested" in politics when, in reference to the "How Many Times a Week Do You Watch the News?" variable, many participants do not watch the news (which could indicate that they are not up-to-date on recent events in regards to politics).
```{r}
g3 <- ggplot(data = na.omit(OOL.sub), aes(PoliticalAffil)) +
  geom_bar(fill = c("red")) +
  labs(x = "", y = "Total Number", title = "What Political Party Do You Affiliate Yourself With?") +
  theme_bw() + 
  theme(axis.text.x  = element_text(angle = 75, vjust = 0.5)) 
g3
```
This is a graph of the variable "What Political Party Do You Affiliate Yourself With?". This graph shows the answers to participants when asked what political party they are. Most participants identified as Democratic and the second most common was Independent.
#Histogram
```{r}
summary(OOL$W1_A11)
hist(OOL$W1_A11, main = "How Many Times a Week Do You Watch the News?")
plot(density(OOL$W1_A11, na.rm = TRUE), main = "How Many Times a Week Do You Watch the News?")
```
This is a histogram of the variable "How Many Times a Week Do You Watch the News?". This graph peaks shows that the most common amount of days that participants watch the news per week are all seven days or they do not watch the news at all during the week. This is shown by the lines in the graph being significantly higher at those two points. This graph would not be considered skewed because of its two peaks at varying points. 

```{r}
summary(OOL$W1_A11)
fivenum(OOL$W1_A11)
median(OOL$W1_A11, na.rm = TRUE)
mean(OOL$W1_A11, na.rm = TRUE)
IQR(OOL$W1_A11, na.rm = TRUE)
```
#Bivariate Graph

##Welfare Rating vs. Political Affiliation
```{r, fig.height=12, fig.width=12}
g1 <- ggplot(data = OOL.sub, aes(x = WatchNews, fill = PoliticalAffil)) +
  geom_bar(position = "fill") + 
  theme_bw()
g1
```
This bivariate graph shows the the association between the amount of days per week the participants watch the news and their political affiliation. The bigger the color per affiliation indicates the more participants that watch the news per week for that political affiliatiate. As shown by the graph, most individuals that watch the news are Democratic and watch the news around four to five days a week.  

##Welfare Rating vs. Interest in Politics
```{r, fig.height=12, fig.width=12}
library(vcd)
mosaic(~WatchNews + InterestPol, data = OOL.sub, shade = TRUE) 

```
  
  This mosaic plot shows the association between how many people are interested in the news and their interest in politics. As displayed in the graph, most individuals that watch the news seven days of the week are very to moderately interested in politics. Most individuals that do not watch the news are not very interest or slightly interested.
  
#Hypothesis 

$H_0:\mu_{Extremely Interested} = \mu_{Very Interested}=\mu_{Moderately Interested} =\mu_{Slightly Interested}=\mu_{Not Interested}$ versus $H_1:\mu_{i} \neq \mu_{j}$ for at least one $i \neq j$ pair.  

Above shows how interested participants are in politics and how often they watch the news. People more interested in politics will most likely watch the news more often. There is no significant difference in the data so the null hypothesis is accepted.

##ANOVA
```{r}
tapply(OOL.sub$Welfare, OOL.sub$WatchNews, mean, na.rm = TRUE)
tapply(OOL.sub$Welfare, OOL.sub$WatchNews, sd, na.rm = TRUE)
library(ggplot2)
ggplot(data = na.omit(OOL.sub), aes(x = WatchNews, y = Welfare, fill= WatchNews))+
  geom_boxplot() +
  theme_bw() +
  guides(fill = FALSE) +
  labs(x = "How many days a week do you watch the news?" , y = "How would you rate people on welfare?", title= "Welfare Rating vs. Days a week News is Watched")
ggplot(data = OOL.sub , aes(x= WatchNews, y= Welfare)) +
  geom_violin() +
  theme_bw() +
  guides(fill = FALSE) +
  labs(x = "WatchNews", y= "Welfare")

#ANOVA Test

mod1 <- aov(Welfare ~ WatchNews, data = OOL.sub)
mod1
summary(mod1)

# Post-hoc test

CIS <- TukeyHSD(mod1)
CIS
opar <- par(no.readonly = TRUE) 
par(mar = c(5, 11, 5, 1))
plot(CIS, las = 1)
par(opar)
mod<- aov(Welfare~WatchNews, data=OOL.sub)
summary(mod)
ci<- TukeyHSD(mod)
ci
plot(ci)
```
According to the above data, there is an association between how much news you watch and welfare rating. Participants that watch the news more days of the week tend to rate people on welfare lower than those that do not watch the news as often.

##Chi-Squared 
Hypothesis:  The Interest in Politics and Political affiliation variables are independent. The alternative would be they are dependent on one another.
```{r}
chi.name <- chisq.test(OOL.sub$InterestPol, OOL.sub$PoliticalAffil)
chi.name$obs
tbl= table(OOL.sub$InterestPol, OOL.sub$PoliticalAffil)
tbl
chisq.test(tbl)
chisq.test(tbl)$exp
p1<- chisq.test(tbl[,c(1,2)])
p2<- chisq.test(tbl[,c(1,3)])
p3<- chisq.test(tbl[,c(1,4)])
p4 <-chisq.test(tbl[,c(2,3)])
p5 <-chisq.test(tbl[,c(3,4)])$p.value
p6 <-chisq.test(tbl[,c(2,4)])
```
According to the above data, the Chi-Squared value is not significant. This means that the null hypothesis is accepted.

##Correlation Coefficient
```{r}
library(ggplot2)
 ggplot(data = OOL.sub, aes(x = Congress, y = Welfare)) + 
   geom_point(color = "purple") +
   theme_bw()
```
This correlation coefficient measures how participants would rate Congress from 1-100 and it's correlation to how participants rate people on welfare from 1-100. 

```{r}
cor(OOL.sub$Congress, OOL.sub$Welfare)
cor.test(OOL.sub$Congress, OOL.sub$Welfare)
ggplot(data = OOL.sub, aes(x = Congress, y = Welfare)) + 
geom_point(color = "purple") +
theme_bw() + 
labs(x = "How would you rate Congress?", y = "How would you rate people on welfare?") +
stat_smooth(method = lm)
```
  
  The correlation of the data is estimated to be 0.3178078. There is no one set direction that the data is graphed. Most of the data is scattered all around the graph. Therefore, there is not a very strong correlation coefficient. There is a slight upward slope in the correlation gap. There are a few outliers, such as a participant rating Congress as 100 and people on welfare between 1-25.

##Regression Assignment
```{r}
mod <- lm(Congress ~ Welfare, data = OOL.sub)
summary(mod)
predict(mod, newdata = data.frame(Welfare = 60))
PV <- predict(mod, newdata = data.frame(Welfare = 60))
PV
```
The prediction for the correlation between how participants rate Congress and how participants rate people on healthcare is 38.41324. It slopes slightly upward on the graph, meaning it is not very strong. Most ratings fall around the middle to lower end of the graph, which means that most people don't give Congress or people on welfare a high rating. 
